On the formation of H$\alpha$ line emission around classical T Tauri star: the disc-wind-magnetosphere hybrid model

### 2006-01-30 TTau_Halpha/kurosawa.tex
replaced the greyscale image for a better contrast one.  RK
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@646 25464f21-6099-402c-b30a-640f1d40d38b
Typo fixed.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@647 25464f21-6099-402c-b30a-640f1d40d38b

We now examine the sensitivity of the model profiles on the wind
collimation or the source displacement parameter $d$. As we can see
from Fig.~\ref{fig:config_discwind}, the disc wind
geometry/collimation is determined by $d$ and the wind launching radii
($R_{\mathrm{wi}}$ and $R_{\mathrm{wo}}$). Here, we fix the values of
$R_{\mathrm{wi}}$ and $R_{\mathrm{wo}}$ as in
Table~\ref{tab:std_discwind_parameters}, and inspect the model
dependency on $d$ alone.  The minimum wind opening angle (measured
from the symmetry axis) is given by
$\theta_{\mathrm{open}}=\arctan\left( d/R_{\mathrm{wi}} \right)$.
Fig.~\ref{fig:discwind_d_effect} shows the profiles computed for $d
= 2~R_{*}$, $7~R_{*}$ and $88~R_{*}$ for the inclination angle
$i=55^{\circ}$.  As the wind becomes more collimated (larger $d$), the
wind launching angle becomes smaller and the wind density is enhanced
towards the symmetry axis ($z$); hence, the wind emission increases.
When the collimation of the wind is small (as in the $d = 2~R_{*}$
case), the P-Cygni absorption is absent from the profile because the
opening angel of the disc wind is greater than the inclination angle.
For the disc wind models presented in this paper, we use $d=44~R_{*}$
to have a moderate amount of wind absorption at a moderate inclination
angle ($i\sim60^\circ$).

@@

    \includegraphics[%
      clip,
      scale=0.45,angle=270]{figures/discwind_hybrid_ha_image.eps}

>>>>

We now examine the sensitivity of the model profiles on the wind
collimation or the source displacement parameter $d$. As we can see
from Fig.~\ref{fig:config_discwind}, the disc wind
geometry/collimation is determined by $d$ and the wind launching radii
($R_{\mathrm{wi}}$ and $R_{\mathrm{wo}}$). Here, we fix the values of
$R_{\mathrm{wi}}$ and $R_{\mathrm{wo}}$ as in
Table~\ref{tab:std_discwind_parameters}, and inspect the model
dependency on $d$ alone.  The minimum wind opening angle (measured
from the symmetry axis) is given by
$\theta_{\mathrm{open}}=\arctan\left( d/R_{\mathrm{wi}} \right)$.
Fig.~\ref{fig:discwind_d_effect} shows the profiles computed for $d
= 2~R_{*}$, $7~R_{*}$ and $88~R_{*}$ for the inclination angle
$i=55^{\circ}$.  As the wind becomes more collimated (larger $d$), the
wind launching angle becomes smaller and the wind density is enhanced
towards the symmetry axis ($z$); hence, the wind emission increases.
When the collimation of the wind is small (as in the $d = 2~R_{*}$
case), the P-Cygni absorption is absent from the profile because the
opening angle of the disc wind is greater than the inclination angle.
For the disc wind models presented in this paper, we use $d=44~R_{*}$
in order to have a moderate amount of wind absorption at a moderate
inclination angle ($i\sim60^\circ$).

@@

%    \includegraphics[%
%      clip,
%      scale=0.45,angle=270]{figures/discwind_hybrid_ha_image.eps}
    \includegraphics[%
	clip,
     scale=0.45, angle=270]{figures/discwind_hybrid_ha_image_grey.eps}
